A ``Dream'' Interface Design

### 2014-11-26 dream-design/dream-design.tex
small fixes

I would also expect all users to be more perform less errors as well as be more satisfied with this ``dream'' interface. As tactile buttons are harder to press, there would be less likelihood that one would be pressed accidentally. Furthermore, studies have shown that most users enjoy tactile feedback \cite{Freeman:2014:TFA:2663204.2663280}.

>>>>

I would also expect all users to perform less errors as well as be more satisfied with this ``dream'' interface. As tactile buttons are harder to press, there would be less likelihood that a button would be pressed accidentally. Furthermore, studies have shown that most users prefer tactile feedback \cite{Freeman:2014:TFA:2663204.2663280}.
